Output Summary

### 2023-04-11 03-post-process/output-plots-children/09-rho-params.Rmd
Fix bug in correlation summary plot
Was including both posterior and prior in summarization -- should have only been posterior

```{r summarize-rho-means}
# get posterior summaries of the mean correlation across all pop pairs
# for each process separately
rho_params1 = match_params(post, "rho", type = "base_only")
rho_params2 = match_params(post, "rho_.+_pr", type = "base_only")
rho_params = rho_params1[!(rho_params1 %in% rho_params2)]
f = function(p) {
  x = rowMeans(post_subset(post, p, matrix = TRUE))
  c(mean = mean(x), sd = sd(x), quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9)))
}
rho_mean_out = t(sapply(rho_params, f))
rho_mean_out = rho_mean_out[order(rho_mean_out[,"mean"]),]

# assign names to the different rho parameters
rho_labels = c(
  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
  "rho_lL_Pb" = "Mean Parr Length",
  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
  "rho_Lphi_Sb_Sa" = "Pre-spawn Survival",
  "rho_Lphi_Rb_Ra" = "BON -> UGR Survival",
  "rho_Lpi" = "Pr(Fall Migrant)",
  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
)
```

@@

* Blue: Mean of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 80% CRI)
* Red: Individual population pairs ("+" = posterior mean, lines = 50% CRI)
* Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness)

>>>>

```{r summarize-rho-means}
# get posterior summaries of the mean correlation across all pop pairs
# for each process separately
rho_params1 = match_params(post, "rho", type = "base_only")
rho_params2 = match_params(post, "rho_.+_pr", type = "base_only")
rho_params = rho_params1[!(rho_params1 %in% rho_params2)]

f = function(p) {
  x = rowMeans(post_subset(post, paste0("^", p, "["), matrix = TRUE))
  c(mean = mean(x), sd = sd(x), quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9)))
}
rho_mean_out = t(sapply(rho_params, f))
rho_mean_out = rho_mean_out[order(rho_mean_out[,"mean"]),]

# assign names to the different rho parameters
rho_labels = c(
  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
  "rho_lL_Pb" = "Mean Parr Length",
  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
  "rho_Lphi_Sb_Sa" = "Pre-spawn Survival",
  "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
  "rho_Lpi" = "Pr(Fall Migrant)",
  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
)
```

@@

* Blue: Mean correlation of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 80% CRI)
* Red: Correlation of individual population pairs ("+" = posterior mean, lines = 50% CRI)
* Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness)
